\documentclass[a4paper,10pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}

% Formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[.]

% Custom commands for formatting
\newcommand{\cvsection}[1]{\section*{\scshape{#1}}}
\newcommand{\cvitem}[2]{\textbf{#1:} #2\\}

% Begin Document
\begin{document}

% Title
\begin{center}
    {\LARGE \textbf{Adebola Oyenuga}}\\[0.5em]
    \href{mailto:debolacodes@gmail.com}{debolacodes@gmail.com} | +234 7066315488 | Lagos, Nigeria\\
    \href{https://linkedin.com/in/adebola.oyenuga}{https://linkedin.com/in/adebola.oyenuga} | \href{https://github.com/debolacodes}{https://github.com/debolacodes}
\end{center}

% Personal Information
\cvsection{Personal Information}
\cvitem{Nationality}{Nigerian}
\cvitem{Languages}{English(), Yoruba (Native, First Language)}

% Education
\cvsection{Education}
\cvitem{2016--2017}{MSc. Systems Engineering (AI and Robotics), University of Lagos, Lagos, Nigeria}
\cvitem{2008--2012}{BSc. Computer Science(Technology), Babcock University, Ilisan Remo}


% Work Experience
\cvsection{Work Experience}
\textbf{Senior Frontend Engineer, Izifin Technologies (2022--Present)}\\
\begin{itemize}[leftmargin=*]
    \item Developed Buy Now Pay Later (BNPL) applications using ReactJS and Redux
(State Management), Tailwind (CSS), ensuring transparent loan management.
    \item Developed an NPM package for integrating Face and ID verification.
Created User Interfaces for BNPL applications using Figma.
	\item Maintained consistent graphic standards across product interfaces for a
polished user experience.
\end{itemize}


\textbf{}\\
\textbf{Analog Teams (analogteams.com), (2021--2022)}\\
\begin{itemize}[leftmargin=*]
    \item Led my software development team in technical planning and development of applications such as ETL, Instant Messaging, and E-commerce solutions.
    \item Managed technical communications with the management team and clients.
    \item Developed a social media app (Native) using Flutter for mobile and ReactJS
for the web app.
\end{itemize}

% Skills
\cvsection{Skills}
\cvitem{Programming}{Javascript, HTML/CSS, Python(Django), LaTeX}
\cvitem{Tools}{Git, Docker, Render, NPM}
\cvitem{Soft Skills}{Leadership, Communication, Teamwork, Problem-Solving}

% Projects
\cvsection{Projects}
\cvitem{Blueskills, Service Hailing App (on Playstore and web) - theblueskills.com}
\cvitem{Datamarket, Loan Application and Customer Intelligence (on Playstore and web). - Datamarket.co}
\cvitem{iziBNPL, BNPL Loan Application and Collection - iziBNPL.com}
\cvitem{Farmz2u, Farming Management Platform - Farmz2u.com}

% Hobbies
\cvsection{Hobbies}
\cvitem{Music}{Playing Guitar, Writing Music.}
\cvitem{Volunteering}{Volunteering for worthy causes in my community.}

% References
\cvsection{References}
Available upon request.

\end{document}
